---
output:
  md_document:
    variant: markdown_github
---

# Purpose

The purpose of this README is to guide readers as well as myself through my code. It provides explanations of functions as well as the reasoning for my code. I aim to code in a functional manner. My project is based on the following topic:


Topic:  Time-Varying correlation comparison of local indices

* Drivers of TV-correlation estimates over time
	
* Comparing Financials, Industrials and Resources - how their dynamic correlations changed over time, perhaps related to interest rate regimes / currency volatilty regimes.

```{r setup, include = FALSE, warning=FALSE}

```


# Loading packages
I have added the packages that I use at the beginning with the exception of rmgarch because it has conflicts with packeages in the tidyverse. I then also source in all my functions from the code folder.

* fmxdat
* tidyverse
* lubridate
* tbl2xts
* rmsfun
* glue
* PortfolioAnalytics
* rugarch
* forecast
* gridExtra
* kableExtra
* MTS
* robustbase
```{r warning=FALSE, include=FALSE}

rm(list = ls()) # Clean your environment:
gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.
library(tidyverse)
library(lubridate)
library(fmxdat)
library(tbl2xts)
library(rmsfuns)
library(glue)
library(PortfolioAnalytics)
library(rugarch)
library(forecast)
library(gridExtra)
library(kableExtra)
# library(rmgarch)
library(MTS)
library(robustbase)
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```
# Data wrangling
I am going to use the data from the practical exam. It is the ALSI and SWIX all share indexes. I am not sure if I should do the analysis on just one of the indexes or both. I start by just using the ALSI but the code that follows allows for the use of either if I want to come back and do the analysis on both. Both indexes are all share indexes so it should not make much of a difference to the results but could be useful for a robustness check if needed but may fall out of the scope of this project.
```{r}
alsi_raw <- read_rds("data/ALSI.rds")
currency <- read_rds("data/USDZAR.rds")
repo_raw <- read.csv("data/HistoricalRateDetail.csv")
```


The following code chunk wrangles and cleans the data. The calculate_sector_returns functions does the following:

* Uses an if function to select a fund (fund_name), extracts the specified sector (sector_name), reweights the weights to sum to 1
* Creates a weights and return xts data frame to use with rmsfun safe portfolio return calculator
* Calculates the sector return and extracts the relevant components (contribution, weights and value)
* Joins the components together to give the final total return for each sector


I then rename the portfolio return to the sector name and join the all the sectors in each index together,
```{r}
#Lets rename the J403 to SWIX and J203 to ALSI and get them as different data sets. 
alsi_df <- alsi_raw %>% 
    rename("ALSI" = "J203", "SWIX"= "J403") %>% 
    mutate(ALSI = coalesce(ALSI,0)) %>% #This is what i should have done it the practical but we live and learn
    mutate(SWIX = coalesce(SWIX,0))

# Now I use a function that incorporates the rmsfuns safe portfolio returns
#I do this for all three sectors and for each fund
#SWIX
swix_fin<- calculate_sector_returns(data = alsi_df, sector_name = "Financials", fund_name = "SWIX") %>% 
    rename("Financials"="PortfolioReturn")

swix_rec<- calculate_sector_returns(alsi_df, "Resources", "SWIX") %>% 
    rename("Resources"="PortfolioReturn")

swix_ind <- calculate_sector_returns(alsi_df, "Industrials", "SWIX") %>% 
    rename("Industrials"="PortfolioReturn")

#ALSI
alsi_fin<- calculate_sector_returns(alsi_df, "Financials", "ALSI") %>% 
    rename("Financials"="PortfolioReturn")

alsi_rec<- calculate_sector_returns(alsi_df, "Resources", "ALSI") %>% 
    rename("Resources"="PortfolioReturn")

alsi_ind <- calculate_sector_returns(alsi_df, "Industrials", "ALSI") %>% 
    rename("Industrials"="PortfolioReturn")


#Now I just need to join them together into two data frames that will then be used to do the garch analysis
swix_portret <- 
    left_join(swix_fin, swix_rec, by = "date") %>% 
    left_join(. , swix_ind, by = "date")

alsi_portret <- 
    left_join(alsi_fin, alsi_rec, by = "date") %>% 
    left_join(., alsi_ind, by = "date")



```

The following cleans and wrangles the repo rate data that was obtained from the SARB so that is matches the datafame above. 
```{r}
# Let's clean up the repo data a bit
repo<- repo_raw %>% 
    slice(-(1:2)) %>%
    rename("repo"= "Description") %>% 
    mutate(date = ymd(Indicator),
           repo = as.numeric(repo)/100) %>% 
    filter(date>ymd(20121231)) %>% 
    select(date, repo)


```
# Garch fitting and ARCH testing
This follows the practical and is complete with respect to the necessary tests of ARCH. From here I only use the ALSI index but I can simply input the swix_portret instead of alsi_portret for all the functions and do the analysis on the SWIX as well.

## Return Persistence
I created a function that essentially wrapped the code to plot the return persistence into a function so I can plot each sector.
```{r warning=FALSE}
#I wrapped the code from the practical into a function where i just need to give the data (as a tbl) sector and it outputs the return persistence graphs
return_persistence_plotter(data = alsi_portret, sector =  "Financials")

```

```{r warning=FALSE}
return_persistence_plotter(alsi_portret, "Resources")

```



```{r warning=FALSE}
return_persistence_plotter(alsi_portret, "Industrials")

```

## Auto correlation functions
```{r warning=FALSE}
#here I again use the ggAcf, theme_fmx and finlot as well as gridExtra to get a nice plot of each sectors autocorrelation
acf_plotter(alsi_portret, "Financials")
```


```{r warning=FALSE}
acf_plotter(alsi_portret, "Resources")

```


```{r warning=FALSE}
acf_plotter(alsi_portret, "Industrials")

```
The ACFs show that there does appear to be strong conditional heteroskedasticity and long memory showing that there is large return persistence but it is also necassary to conduct a formal box test to prove it.

## Box tests
I started by writing a function that could output the box test for each sector but then decided to rather include a for loop that gets the relavant statistics for each sector and rbinds them together and outputs a single table.
```{r}
# box_test<- function(data, sector){
#     if(sector == "Financials"){
#         play_df<- data %>%
#             select(date, Financials) %>%
#             tbl_xts()
#     }
# 
#     if(sector == "Resources"){
#         play_df<- data %>%
#             select(date, Resources) %>%
#             tbl_xts()
#     }
# 
#     if(sector == "Industrials"){
#         play_df<- data %>%
#             select(date, Industrials) %>%
#             tbl_xts()
#     }
#  box_test_result <- Box.test(coredata(play_df^2), type = "Ljung-Box", lag = 12)
# 
#   # Create a data frame with the test result
#   result_df <- data.frame(
#     TestStatistic = box_test_result$statistic,
#     PValue = box_test_result$p.value,
#     Lag = box_test_result$parameter
#   )
# 
#   # Print the data frame as a nice table using kable
#   kable(result_df, caption =glue("Ljung-Box Test Results: {sector}"))
# }
# box_test(alsi_portret, "Financials")
```


```{r}


box_test_foo(alsi_portret, sectors = c("Financials", "Resources", "Industrials"))
```
The p-value for all sectors as extremely small therefore the results of the box tests rejects the null hypothesis that there are no ARCH effects. This is sufficient motivation to control for the conditional heteroskedasticity. 

## Rugarch
Below I wrap the model comparison code from the practical in a function so that I can then use lapply to apply the function to each sector and then use do.call to combine the results into a single table. 

```{r}

# Apply the GARCH model comparison to all sectors
sectors <- c("Financials", "Resources", "Industrials")
garch_results <- lapply(sectors, function(sector) garch_model_comparison(alsi_portret, sector))

# Combine the results into a single data frame
combined_results <- do.call(rbind, garch_results)

# Print the combined results as a nice table using kable
kable(combined_results, caption = "GARCH Model Comparison Results")

```

apARCH performs the best for Financials and Resources so we will use that for the fit. 

I think it could be informative to show the news impact curves to highlight the differences between the different types of model specs
```{r}


```


# Multivariate
Following the literature comparisons between DCC, aDCC GO-GARCH are used.

## Interest rate regime
A slight detour, I want to stratify the sample to get high and low volatility in the repo. This follows the additional practical.
```{r}
Idxs <- alsi_portret %>% 
    gather(sector, ret, -date) %>% # needs to be in long format
    mutate(Year = format(date, "%Y")) %>% # I am using monthly data so I need a new year column, The rest follows from the practical
    group_by(sector) %>% 
    mutate(Top = quantile(ret, 0.99), Bot = quantile(ret, 0.01)) %>% 
  
  mutate(ret = ifelse(ret > Top, Top, 
                         
                         ifelse(ret < Bot, Bot, ret))) %>% ungroup()

repoSD <- repo %>% 
    mutate(Year = format(date, "%Y")) %>% 
    arrange(date) %>% 
  
  group_by(Year) %>% summarise(SD = sd(repo)*sqrt(12)) %>% 
  
 
  mutate(TopQtile = quantile(SD, 0.75, na.rm = TRUE),
         
         BotQtile = quantile(SD, 0.25, na.rm = TRUE))

Hi_Vol <- repoSD %>% filter(SD > TopQtile) %>% pull(Year)
Low_Vol <- repoSD %>%  filter(SD < BotQtile) %>% pull(Year)


Perf_comparisons <- function(Idxs, Ys, Alias){
  Unconditional_SD <- 
    
  Idxs %>% 
    
    group_by(sector) %>% 
    
    mutate(Full_SD = sd(ret) * sqrt(12)) %>% 
    
    filter(Year %in% Ys) %>% 
    
    summarise(SD = sd(ret) * sqrt(12), across(.cols = starts_with("Full"), .fns = max)) %>% 
    
    arrange(desc(SD)) %>% mutate(Period = Alias) %>% 
    
    group_by(sector) %>% 
    
    mutate(Ratio = SD / Full_SD)
    
    Unconditional_SD
  
}

perf_hi <- Perf_comparisons(Idxs, Ys = Hi_Vol, Alias = "High_Vol")

perf_lo <- Perf_comparisons(Idxs, Ys = Low_Vol, Alias = "Low_Vol")

kableExtra::kable(perf_hi)
kableExtra::kable(perf_lo)
```
Now that I have the volatility periods I can get the time-varying correlations with the three different methodologies to compare. First I import the renammingdcc function so that I can easily extract the correlations to plot.



## DCC 
Below I follow the practical to estimate the DCC between sectors but for ease of extraction I rename the sectors and then join the ZAR/USD exchange rate as it will also be used to in the analysis. The inclusion of the exchange rate follows Fakhfekh et al,. (2020) and Ali et al,. (2022).
```{r}
library(tidyverse)
xts_rtn <- alsi_portret %>% 
    rename("FIN" = "Financials", "REC"= "Resources", "IND" = "Industrials") %>% # This is to get more easible readible paies
    left_join(., currency %>% mutate(EX = value/lag(value)-1) %>% filter(date > dplyr::first(date)) %>% select(date, EX), by = "date") %>% 
    tbl_xts()

```

```{r warning=FALSE}
library(rmgarch)
#Now set the specifications for both the dcc and go-garch
#a) Set the Univaariate GARCH  spec (using aparch from the table above)
uspec <- ugarchspec(variance.model = list(model = "apARCH", 
    garchOrder = c(1, 1)), mean.model = list(armaOrder = c(1, 
    0), include.mean = TRUE), distribution.model = "sstd")

# b) repeat the uspec n times 
multi_univ_garch_spec <- multispec(replicate(ncol(xts_rtn), uspec))

#c) now we set the DCC specs
spec.dcc = dccspec(multi_univ_garch_spec, dccOrder = c(1, 1), 
    distribution = "mvnorm", lag.criterion = c("AIC", "HQ", "SC", 
        "FPE")[1], model = c("DCC", "aDCC")[1]) # maybe come back and use aDCC and comparison between the three is prominant in the literature

# d) Enable clustering for speed:
cl = makePSOCKcluster(10)


# Step 2
# Fit the univariate series for each column
multf = multifit(multi_univ_garch_spec, xts_rtn, cluster = cl)

# Now we can use multf to estimate the dcc model using our
# dcc.spec:
fit.dcc = dccfit(spec.dcc, data = xts_rtn, solver = "solnp", 
    cluster = cl, fit.control = list(eval.se = FALSE), fit = multf)

# Testing the models fit: Tsay (2014)
RcovList <- rcov(fit.dcc)  # This is now a list of the monthly covariances of our DCC model series.
covmat = matrix(RcovList, nrow(xts_rtn), ncol(xts_rtn) * ncol(xts_rtn), 
    byrow = TRUE)
mc1 = MCHdiag(xts_rtn, covmat)



# Now to save the time-varying correlations as specified by
# the DCC model, it again requires some gymnastics from our
# side.  First consider what the list looks like:
dcc.time.var.cor <- rcor(fit.dcc)
# print(dcc.time.var.cor[, , 1:3])

# Now again follow the code in the prac to ensure we end up with bivariate pairs
# rather than lists of matrices
dcc.time.var.cor <- aperm(dcc.time.var.cor, c(3, 2, 1))
dim(dcc.time.var.cor) <- c(nrow(dcc.time.var.cor), ncol(dcc.time.var.cor)^2)

#For ease of extraction we call on the renaming dcc function 
dcc.time.var.cor <- renamingdcc(ReturnSeries = xts_rtn, DCC.TV.Cor = dcc.time.var.cor)
```

```{r warning=FALSE}


#Now lets get the two plots
#Starting with financials
dcc_plot1 <- ggplot(dcc.time.var.cor %>% filter(grepl("FIN_", Pairs), 
    !grepl("_FIN", Pairs))) + geom_line(aes(x = date, y = Rho, 
    colour = Pairs)) + theme_fmx() + ggtitle("Dynamic Conditional Correlations: Financials")+
       theme(axis.title.x = element_blank()) + 
  annotate("rect", xmin = as.Date("2013-01-01"), xmax = as.Date("2013-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2018-01-01"), xmax = as.Date("2018-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2020-01-01"), xmax = as.Date("2020-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2021-01-01"), xmax = as.Date("2021-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2022-01-01"), xmax = as.Date("2022-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2023-01-01"), xmax = as.Date("2023-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3)


#Now Resources
dcc_plot2 <- ggplot(dcc.time.var.cor %>% filter(grepl("REC_", Pairs), 
    !grepl("_REC", Pairs))) + geom_line(aes(x = date, y = Rho, 
    colour = Pairs)) + theme_fmx() + ggtitle("Dynamic Conditional Correlations: Resources")+ 
  annotate("rect", xmin = as.Date("2013-01-01"), xmax = as.Date("2013-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2018-01-01"), xmax = as.Date("2018-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2020-01-01"), xmax = as.Date("2020-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2021-01-01"), xmax = as.Date("2021-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2022-01-01"), xmax = as.Date("2022-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2023-01-01"), xmax = as.Date("2023-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3)

# Lastly for Industrials
dcc_plot3 <- ggplot(dcc.time.var.cor %>% filter(grepl("IND_", Pairs), 
    !grepl("_IND", Pairs))) + geom_line(aes(x = date, y = Rho, 
    colour = Pairs)) + theme_fmx() + ggtitle("Dynamic Conditional Correlations: Industricals")+ 
  annotate("rect", xmin = as.Date("2013-01-01"), xmax = as.Date("2013-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2018-01-01"), xmax = as.Date("2018-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2020-01-01"), xmax = as.Date("2020-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2021-01-01"), xmax = as.Date("2021-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2022-01-01"), xmax = as.Date("2022-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2023-01-01"), xmax = as.Date("2023-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3)


finplot(dcc_plot1)

```

```{r warning=FALSE}
finplot(dcc_plot2)
```

```{r warning=FALSE}
finplot(dcc_plot3)
```

## aDCC
I follow exactly the same process, only changing the model spec to aDCC.
```{r warning=FALSE}
spec.adcc = dccspec(multi_univ_garch_spec, dccOrder = c(1, 1), 
    distribution = "mvnorm", lag.criterion = c("AIC", "HQ", "SC", 
        "FPE")[1], model = c("DCC", "aDCC")[2]) # I now use the aDCC model spec

# d) Enable clustering for speed:
cl = makePSOCKcluster(10)


# Step 2
# Fit the univariate series for each column
multf = multifit(multi_univ_garch_spec, xts_rtn, cluster = cl)

fit.adcc = dccfit(spec.adcc, data = xts_rtn, solver = "solnp", 
    cluster = cl, fit.control = list(eval.se = FALSE), fit = multf)

# Testing the models fit: Tsay (2014)
RcovList <- rcov(fit.dcc)  # This is now a list of the monthly covariances of our DCC model series.
covmat = matrix(RcovList, nrow(xts_rtn), ncol(xts_rtn) * ncol(xts_rtn), 
    byrow = TRUE)
mc1 = MCHdiag(xts_rtn, covmat)



# Now to save the time-varying correlations as specified by
# the DCC model, it again requires some gymnastics from our
# side.  First consider what the list looks like:
adcc.time.var.cor <- rcor(fit.adcc)
# print(adcc.time.var.cor[, , 1:3])

# Now again follow the code in the prac to ensure we end up with bivariate pairs
# rather than lists of matrices
adcc.time.var.cor <- aperm(adcc.time.var.cor, c(3, 2, 1))
dim(adcc.time.var.cor) <- c(nrow(adcc.time.var.cor), ncol(adcc.time.var.cor)^2)

#For ease of extraction we call on the renaming dcc function 
adcc.time.var.cor <- renamingdcc(ReturnSeries = xts_rtn, DCC.TV.Cor = adcc.time.var.cor)
```

```{r warning=FALSE}
adcc_plot1 <- ggplot(dcc.time.var.cor %>% filter(grepl("FIN_", Pairs), 
    !grepl("_FIN", Pairs))) + geom_line(aes(x = date, y = Rho, 
    colour = Pairs)) + theme_fmx() + ggtitle("Assymetric Dynamic Conditional Correlations: Financials")+
       theme(axis.title.x = element_blank())+ 
  annotate("rect", xmin = as.Date("2013-01-01"), xmax = as.Date("2013-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2018-01-01"), xmax = as.Date("2018-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2020-01-01"), xmax = as.Date("2020-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2021-01-01"), xmax = as.Date("2021-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2022-01-01"), xmax = as.Date("2022-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2023-01-01"), xmax = as.Date("2023-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3)


#Now Resources
adcc_plot2 <- ggplot(dcc.time.var.cor %>% filter(grepl("REC_", Pairs), 
    !grepl("_REC", Pairs))) + geom_line(aes(x = date, y = Rho, 
    colour = Pairs)) + theme_fmx() + ggtitle("Assymetric Dynamic Conditional Correlations: Resources")+ 
  annotate("rect", xmin = as.Date("2013-01-01"), xmax = as.Date("2013-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2018-01-01"), xmax = as.Date("2018-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2020-01-01"), xmax = as.Date("2020-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2021-01-01"), xmax = as.Date("2021-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2022-01-01"), xmax = as.Date("2022-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2023-01-01"), xmax = as.Date("2023-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3)

# Lastly for Industrials
adcc_plot3 <- ggplot(dcc.time.var.cor %>% filter(grepl("IND_", Pairs), 
    !grepl("_IND", Pairs))) + geom_line(aes(x = date, y = Rho, 
    colour = Pairs)) + theme_fmx() + ggtitle("Assymetric Dynamic Conditional Correlations: Industricals")+ 
  annotate("rect", xmin = as.Date("2013-01-01"), xmax = as.Date("2013-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2018-01-01"), xmax = as.Date("2018-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2020-01-01"), xmax = as.Date("2020-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2021-01-01"), xmax = as.Date("2021-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2022-01-01"), xmax = as.Date("2022-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2023-01-01"), xmax = as.Date("2023-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3)


```

```{r warning=FALSE}
finplot(adcc_plot1)
```

```{r warning=FALSE}
finplot(adcc_plot2)

```

```{r warning=FALSE}
finplot(adcc_plot3)

```

## GO-GARCH
Lastly I fit a GO-GARCH, again folowing the practical, using the same univariate GARCH spec.
```{r warning=FALSE}



spec.go <- gogarchspec(multi_univ_garch_spec, 
                       distribution.model = 'mvnorm', 
                       ica = 'fastica') # Note: we use the fastICA
cl <- makePSOCKcluster(10)
multf <- multifit(multi_univ_garch_spec, xts_rtn, cluster = cl)

fit.gogarch <- gogarchfit(spec.go, 
                      data = xts_rtn, 
                      solver = 'hybrid', 
                      cluster = cl, 
                      gfun = 'tanh', 
                      maxiter1 = 40000, 
                      epsilon = 1e-08, 
                      rseed = 100)

gog.time.var.cor <- rcor(fit.gogarch)
gog.time.var.cor <- aperm(gog.time.var.cor,c(3,2,1))
dim(gog.time.var.cor) <- c(nrow(gog.time.var.cor), ncol(gog.time.var.cor)^2)
# Finally:
gog.time.var.cor <-
renamingdcc(ReturnSeries = xts_rtn, DCC.TV.Cor = gog.time.var.cor)

```
```{r warning=FALSE}
go1 <- ggplot(gog.time.var.cor %>% filter(grepl("FIN_", Pairs), 
    !grepl("_FIN", Pairs))) + geom_line(aes(x = date, y = Rho, 
    colour = Pairs)) + theme_fmx() + ggtitle("Go-GARCH: Financials")+ 
  annotate("rect", xmin = as.Date("2013-01-01"), xmax = as.Date("2013-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2018-01-01"), xmax = as.Date("2018-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2020-01-01"), xmax = as.Date("2020-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2021-01-01"), xmax = as.Date("2021-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2022-01-01"), xmax = as.Date("2022-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2023-01-01"), xmax = as.Date("2023-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3)

go2 <- ggplot(gog.time.var.cor %>% filter(grepl("REC_", Pairs), 
    !grepl("_REC", Pairs))) + geom_line(aes(x = date, y = Rho, 
    colour = Pairs)) + theme_fmx() + ggtitle("Go-GARCH: Resources")+ 
  annotate("rect", xmin = as.Date("2013-01-01"), xmax = as.Date("2013-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2018-01-01"), xmax = as.Date("2018-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2020-01-01"), xmax = as.Date("2020-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2021-01-01"), xmax = as.Date("2021-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2022-01-01"), xmax = as.Date("2022-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2023-01-01"), xmax = as.Date("2023-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3)

go3 <- ggplot(gog.time.var.cor %>% filter(grepl("IND_", Pairs), 
    !grepl("_IND", Pairs))) + geom_line(aes(x = date, y = Rho, 
    colour = Pairs)) + theme_fmx() + ggtitle("Go-GARCH: Industrials")+ 
  annotate("rect", xmin = as.Date("2013-01-01"), xmax = as.Date("2013-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2018-01-01"), xmax = as.Date("2018-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2020-01-01"), xmax = as.Date("2020-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2021-01-01"), xmax = as.Date("2021-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "blue", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2022-01-01"), xmax = as.Date("2022-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3) +
  annotate("rect", xmin = as.Date("2023-01-01"), xmax = as.Date("2023-12-31"), 
           ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.3)

```

```{r warning=FALSE}
finplot(go1)
```

```{r warning=FALSE}
finplot(go2)
```

```{r warning=FALSE}
finplot(go3)
```








